Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/tool.tex
added complexity analysis to 'tool.tex'

% Routing Tree Algorithm
\par To calculate the routing trees, we use an extended version of the
BGPSim algorithm developed by Gil et. al in \cite{quicksand}. This
component of \toolname{} addresses several limitations that prevented
us using BGPSim directly: (1) BGPSim returns a set of ASes for each
path it considers but not the order in which they are visited; (2)
Once routing trees are determined, they cannot be accessed later
without recalculation; (3) BGPSim relies on the outdated
parallelization framework DryadLinq for C\#. To address these issues,
we implemented our routing simulation in
Python. \Ben[inline]{Why does BGPSim not return ordered paths, this
  seems trivial, but I don't know the implementation details, was it
  just an oversight or did you do something cool?}\toolname{} returns
ordered paths from its routing trees, saves routing trees to disk
after calculation, and is parallelized with MPI via the mpi4py
library. These improvements have the added benefit of yielding a cross
platform routing tree algorithm that is portable to most
hardware.

\Steph[inline]{Where is the code available?  What about the dataset of routing trees?  that is one of our big contributions.}

@@

\Steph[inline]{A brief complexity analysis, even just in words, would help, as woulddata on how long the computations take.  Complexity discussion here, timing data in Experiments?}

>>>>

% Routing Tree Algorithm
\par To calculate the routing trees, we use an extended version of the
BGPSim algorithm developed by Gil et. al in \cite{quicksand}. This
component of \toolname{} addresses several limitations that prevented
us using BGPSim directly: (1) BGPSim returns a set of ASes for each
path it considers but not the order in which they are visited; (2)
Once routing trees are determined, they cannot be accessed later
without recalculation; (3) BGPSim relies on the outdated
parallelization framework DryadLinq for C\#. To address these issues,
we implemented our routing simulation in
Python. \Ben[inline]{Why does BGPSim not return ordered paths, this
  seems trivial, but I don't know the implementation details, was it
  just an oversight or did you do something cool?}\toolname{} returns
ordered paths from its routing trees, saves routing trees to disk
after calculation, and is parallelized with MPI via the mpi4py
library. These improvements have the added benefit of yielding a cross
platform routing tree algorithm that is portable to most
hardware. The source code for \toolname{} and all datasets are publicly available at [URL blinded for peer review].

@@

Calculating routing trees for the entire AS graph takes time proportional to the $|V|^2$ where $|V|$ is the total number of ASes; calculating chokepoint potential takes $|V|^2D$ where $D$ is the average depth of a routing tree. For example,
it took about 12 wall clock hours to compute all of the routing trees for the Jan. 2017 dataset, running on 4 Intel Xeon E5-2680 V4 CPUs.  For each dataset, this is a one-time cost because the routing trees are stored externally.  [URL blineded for peer review]
